\section{Data description}

In this section, we present a brief description of the data that we plan to analyze using our proposed visual system. 

\textbf{Taxi Trip Data :} NYC taxi trip data is spatio-temporal multivariate data. The data consists of monthly taxi trip details of three types of taxi - Yellow, Green, For-hire over the years. Each monthly trip data consists of the location of the pickup and dropoff points for each trip. Datasets are huge. For this work, we took into consideration three months of Taxi trips data from October to December, 2018. Each month consists information of approximately 30M of taxi trips. 

\textbf{Twitter Data :} Twitter data has been used in Sentiment classification;  a well-researched topic. In this project, our aim is to build a general sentiment classifier and utilize that to analyze Twitter data over popular news articles to predict the general public sentiment resulting from them. In addition to sentiment classifier we also propose a topic modeling algorithm to extract relevant topics related to various events such as Halloween, Thanksgiving and so on. For the analysis, we used NYC twitter data from October to December, 2018. Each month consists of around 1.2M tweets. The topic and public sentiment derived from these classified tweets are then used to correlate urban taxi trip behavior. In general, the Twitter data are spatio-temporal consisting of the actual tweet, time, and location. 


% To train our initial sentiment classifier, we will use the Kaggle Sentiment140 Dataset of 1.6 Million tweets and use that to classify relevant tweets extracted from the Twitter API. We plan to apply for the Academic Research Product track which allows users to download 10 million tweets a month. The public sentiment derived from classified tweets will then be used to correlate urban taxi trip behavior. 